Single-fluorophore orientation determination with multiview polarized illumination: modeling and microscope design

### 2017-09-05 paper/paper/paper.tex
Clarifying Rudolf's change.

Also note that the detection efficiency can take its maximum range of values
when $B$ takes its maximum value, i.e. when
$\alpha=\arccos\left(\frac{1}{\sqrt{3}}\right) \approx 54.7^{\circ}$. When
$\alpha = \frac{\pi}{2}$ the detection efficiency is $\frac{1}{2}$ for all
fluorophore orientations and when $\alpha = 0$ the detection efficiency is zero
for all fluorophore orientations, so we expect there to be an intermediate value
of $\alpha$ where the detection efficiency takes its maximum range. This means
that the maximum modulation of detected intensities will occur when we choose a
detection objective with $\alpha \approx 54.7^{\circ}$.

>>>>

Also note that the detection efficiency can take its maximum range of values
when $B$ takes its maximum value, i.e. when
$\alpha=\arccos\left(\frac{1}{\sqrt{3}}\right) \approx 54.7^{\circ}$. This means
that the maximum modulation of detected intensities will occur when we choose a
detection objective with $\alpha \approx 54.7^{\circ}$.
